Making Sequential Programs Deterministic

### 2019-04-04 paper.tex
moving text around
Edits in section 2.1
expts
Edits in section 2.2
references
experiments: NONDEX on Randoop
Randoop case study
Edits in sections 2-2.3
Threats to validity, and changes suggested by Jason
Draft of abstract

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption

\usepackage{url}

\usepackage{color}
%% Comment out one of these two definitions.
% \newcommand{\todo}[1]{\relax}
\newcommand{\todo}[1]{{\color{red}\bfseries [[#1]]}}

% \|name| or \mathid{name} denotes identifiers and slots in formulas
\def\|#1|{\mathid{#1}}
\newcommand{\mathid}[1]{\ensuremath{\mathit{#1}}}
% \<name> or \codeid{name} denotes computer code identifiers
\def\<#1>{\codeid{#1}}
\protected\def\codeid#1{\ifmmode{\mbox{\sf{#1}}}\else{\sf #1}\fi}
\protected\def\codeid#1{\ifmmode{\mbox{\ttfamily{#1}}}\else{\ttfamily #1}\fi}
\protected\def\codeid#1{\ifmmode{\mbox{\smaller\ttfamily{#1}}}\else{\smaller\ttfamily #1}\fi}

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
\todo{Text of abstract \ldots.}
\end{abstract}

@@

\input{introduction.tex}
\input{design.tex}

@@

%% Bibliography
%\bibliographystyle{ACM-Reference-Format.bst}
\bibliography{paper,bibstring-unabbrev,testing,crossrefs}

>>>>

%% Some recommended packages.
\usepackage{proof}
\usepackage{amsmath,amssymb,amsthm,textcomp}

\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{wrapfig}
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption

\usepackage{url}
\usepackage{xspace}

\usepackage{fancyvrb}
\fvset{fontsize=\smaller}

\usepackage{color}

\usepackage{cleveref}
\usepackage{hyperref}

\input{macros.tex}

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
\todo{The title ``Making Sequential Programs Deterministic'' is misleading
  because our tool doesn't transform programs, though it does help
  programmers transform programs.}

When a program is nondeterministic, it is difficult to test and debug.
Nondeterminism can occur even in sequential programs, for example as a
result of iterating over the elements of a hash table.

We have created a type system for determinism.  A type checker warns if a
program is nondeterministic or verifies that the program is deterministic.
The key ideas in the type system are type qualifiers for nondeterminism,
order-nondeterminism, and determinism; type well-formedness rules to
restrict the typings for collections; and enhancements to polymorphism that
improve precision when analyzing collection operations.

We implemented our type system for Java.  In a case study, it found
previously-unknown nondeterminism errors in a program that had been heavily
vetted by its developers.  In an experiment, it found all of the
non-concurrency-related nondeterminism that was found by other tools.

\end{abstract}

@@

\input{introduction.tex}
\input{design.tex}
\input{java-design.tex}
\input{randoop-case-study}
\input{experiments.tex}
\input{threats}
\input{related}
\input{conclusion}

@@

%% Bibliography
%\bibliographystyle{ACM-Reference-Format.bst}
\clearpage
\bibliography{paper,bibstring-unabbrev,testing,crossrefs}
